# Africa 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("code/map-1.R", print.eval = TRUE)

```

All chapters start with a first-level heading followed by your chapter title, like the line above. There should be only one first-level heading (`#`) per .Rmd file...

## Madagascar

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("code/map-2.R", print.eval = TRUE)

```

All chapter sections start with a second-level (`##`) or higher heading followed by your section title, like the sections above and below here. You can have as many as you want within a chapter.

### aaaaa

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the shorter `{-}` at the end of the heading, like in this section.

```{r, echo=FALSE}
value <- c(1:9)

library(ggplot2)
library(emojifont)
df <- data.frame(
  x = rep(seq(2, 15, 6.5), 3),
  y = c(rep(15, 3), rep(10.5, 3), rep(6, 3)),
  h = rep(4.25, 9),
  w = rep(6.25, 9),
  value = value,
  info = c("Population",
           "Number of HHs",
           "Average HH size",
           "Sex ratio (men/women)",
           "Percentage living in urban areas",
           "Child dependency ratio",
           "Old age dependency ratio",
           "Total fertility rate",
           ""),
  font_family = c(rep("fontawesome-webfont", 8),
                  "EmojiOne"),
  color = factor(1:9)
)

ggplot(df, aes(x, y, height = h, width = w, label = info)) +
  ## Create the tiles using the `color` column
  geom_tile(aes(fill = color)) +
  ## Add the numeric values as text in `value` column
  geom_text(color = "white", fontface = "bold", size = 7,
            aes(label = value, x = x - 2.9, y = y + 1), hjust = 0) +
  ## Add the labels for each box stored in the `info` column
  geom_text(color = "white", fontface = "bold", size = 2.9,
            aes(label = info, x = x - 2.9, y = y - 1), hjust = 0) +
  coord_fixed() +
  scale_fill_brewer(type = "qual", palette = c("Paired")) +
  ## Use `geom_text()` to add the icons by specifying the unicode symbol.
# geom_text(size = 20, aes(label = icon, family = font_family,
#                           x = x + 1.5, y = y + 0.5), alpha = 0.25) +
  theme_void() +
  guides(fill = "none")
```